### 2024-08-19 paper.tex
an isomorphism

% \par TODO: where does this paragraph go?
% Let \(W_\mu\) denote the Springer fiber at \(J(\mu)\), and let \((W_{\mu, d})_d\) be the irreducible components.
% We remark that the Springer fiber at \(PJ(\mu)P^{-1}\) is \(PW_\mu\), and its irreducible components are \((PW_{\mu, d})_d\).

@@

>>>>

@@

Let \(\mu\) be the shape of the Jordan basis given in the previous lemma.
Let \(X_\mu\) be the Springer fiber at \(J(\mu)\).

\begin{lemma}
    \(U_{I, (\rho_i)} \cong B_{I, (\rho_i)} \times X_\mu\).
\end{lemma}
\begin{proof}
    For \(b \in B_{I, (\rho_i)}\), let \(P_b\) be the change-of-basis matrix, with columns given by the Jordan basis of the previous lemma, so that \(J(\mu) = P_b^{-1} A_{0,b} P_b\).
    From looking at the Jordan basis of the previous lemma (the basis can be expressed in terms of \(A, \lambda, e_{ij}, f_i, I, \rho_i, b\)), it is clear that the map \(P : B_{I, (\rho_i)} \to \GL_{m + n}\), given by \(b \mapsto P_b\), is algebraic.
    \par Now, we remark that the Springer fiber at \(A_{0,b}\) is simply \(\{P_b U : U \in X_\mu\}\).
    This gives us the isomorphism \(B_{I, (\rho_i)} \times X_\mu \to U_{I, (\rho_i)}\).
    \[(b, U) \mapsto (P_b J(\mu) P_b^{-1}, P_b U),\]
    with inverse
    \[(A_{0,b}, U) \mapsto (b, P_b^{-1} U).\]
\end{proof}
At last we have reached the base of our recursive procedure, and we begin to propagate upwards.
